---
title: "080921_meeting"
author: "Jacob Wynne"
date: "8/6/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Calibration

All models with the exception of FLake are calibrated with LHC to under 2 RMSE. There are currently a few bugs being worked out in the LHC script which will allow flake to fall under to 2 RMSE threshold. Other metrics such as NSE, r, bias and MAE all match up relatively well between models, with the exception of a positive bias in FLake and a large range of MAE values between models. 

In terms of thermal metrics, the observed data tracks both Schmidt stability and thermocline depth relatively well. Unfortunately, observations are not yet calculable for the batch thermal metrics calculated but likely will be in the near future. 

Once observations are calculated for all thermal metrics and validation is carried out, a possibility is to weight each model based on its performance in relation to observations. The weight could be calculated by taking the average distance from each model output to the observation over the course of the validation period. 

* Would model weighting cause the uncertainty analyses to become overly complex or defeat the purpose of the uncertainty? 
* Consensus is that weighting would overcomplicate for this particular study and lead to unwanted issues when looking at uncertainty. 




```{r, include = FALSE}
library(LakeEnsemblR)
library(lubridate)
library(plyr)
library(gotmtools)
library(ggplot2)
library(ggpubr)
library(dplyr)
library(rLakeAnalyzer)
library(reshape)
library(RColorBrewer)
```


```{r, echo=FALSE,results='hide',fig.keep='all'}
Sys.setenv(TZ = "UTC")

# remotes::install_github("tadhg-moore/LakeEnsemblR", ref = "flare")
# remotes::install_github("tadhg-moore/gotmtools", ref = "yaml")
# remotes::install_github("tadhg-moore/LakeEnsemblR", ref = "flare")
# remotes::install_github("aemon-j/gotmtools", ref = "yaml", force = TRUE)


# Set working directory
getwd()
setwd("~/Dropbox/sunapee_LER_projections/LER_calibration/")

# Set config file & models
config_file <- 'LakeEnsemblRsun.yaml'
model <- c("FLake")
ncdf <- "output/ensemble_output.nc"

config_file

# mantemp <- read.csv("Data/manual_buoy_temp_hrz.csv")
# str(mantemp)
# mantemp$datetime <- as.POSIXct(mantemp$datetime, format = "%Y-%m-%d %H:%M:%S")
# write.csv(mantemp, "Data/manual_buoy_temp_hrz_psx.csv", row.names = FALSE)

# LHC - Calibration ----

yaml <- read_yaml(config_file)
configr::read.config(config_file)
yaml$time$start <- "2005-06-27 00:00:00"
yaml$time$stop <- "2010-01-01 00:00:00"
# yaml$time$start <- "2007-06-11 12:00:00"
# yaml$time$stop <- "2012-01-01 00:00:00"
yaml$input$ice$use <- TRUE
yaml$output$time_step <- 24
yaml$output$time_unit <- "hour"
write_yaml(yaml, config_file)
num <- 500
spin_up <- 190
out_f <- "calibration_results_FLake_071621"

cmethod <- "LHC"
model <- c("FLake", "GLM", "Simstrat", "GOTM", "MyLake")

folder <- "."
dir.create(out_f, showWarnings = FALSE)


# Run LER and inspect default output
export_config(config_file, model)

run_ensemble(config_file = config_file, model = model)

#file.rename("output/ensemble_output.nc", "output/ensemble_output_all_models.nc")

# plot heatmap
plot_heatmap(ncdf, model = model) +
  scale_colour_gradientn(limits = c(0, 32),
                         colours = rev(RColorBrewer::brewer.pal(11, "Spectral"))) + theme_classic()

plot_ensemble(ncdf, model = model, var = "ice_height")

fit <- calc_fit(ncdf, model = model, spin_up = spin_up)
fit

# out <- analyze_ncdf(ncdf, model, spin_up = 190)
# out$stats 

## Plot residuals
plist <- plot_resid(ncdf = "output/ensemble_output.nc", var = "temp")
ggarrange(plotlist = plist)

```


```{r, eval = FALSE}

param_file <- "calibration_results_FLake_071621/params_FLake_LHC_202107161729.csv"

cali_ensemble(config_file, num = num, cmethod = cmethod, parallel = FALSE, model = model, folder = ".",
              spin_up = spin_up, job_name = model, out_f = out_f)

cal_files <- list.files(out_f, full.names = TRUE)
cal_files <- cal_files[c(1,2)]

res <- load_LHC_results(config_file = config_file, model = model, res_files = cal_files)
dim(res[[model]])


df <- plyr::ldply(res, function(x) {
  df <- x[, -c(3:7)]
  reshape2::melt(df, id.vars = c("par_id", "rmse"))
}, .id = "model")
df$id_no <- as.numeric(gsub(".*?([0-9]+).*", "\\1", df$par_id))

bst_par <- df$id_no[which.min(df$rmse)]
sub <- df[df$id_no == bst_par, ]
sub

p1 <- ggplot(df) +
  geom_point(aes(value, rmse)) +
  facet_wrap(model~variable, scales = "free_x") +
  geom_hline(yintercept = 2, linetype = "dashed") +
  ylab("RMSE (\u00B0C)") +
  geom_vline(data = sub, aes(xintercept = value)) +
  geom_hline(yintercept = 3.5, color = "red", linetype = "dashed") +
  # coord_cartesian(ylim = c(1, 4)) +
  # scale_x_log10() +
  theme_classic(base_size = 16)
p1

#
sub <- df[df$id_no == bst_par, ]
# sub <- df[df$id_no == 1, ] # Use this to try other parameter combinations
sub

yaml$model_parameters$FLake$`LAKE_PARAMS/c_relax_C` <- sub$value[3]
yaml$scaling_factors$FLake$wind_speed <- sub$value[1]
yaml$scaling_factors$FLake$swr <- sub$value[2]

# yaml$scaling_factors$GLM$wind_speed <- sub$value[1]
# yaml$scaling_factors$GLM$swr <- sub$value[2]
# yaml$model_parameters$GLM$`sediment/sed_temp_mean` <- c(sub$value[3], sub$value[4])

# yaml$scaling_factors$GOTM$wind_speed <- sub$value[1]
# yaml$scaling_factors$GOTM$swr <- sub$value[2]
# yaml$model_parameters$GOTM$`turbulence/turb_param/k_min` <- sub$value[3]

# yaml$scaling_factors$Simstrat$wind_speed <- sub$value[1]
# yaml$scaling_factors$Simstrat$swr <- sub$value[2]
# yaml$model_parameters$Simstrat$`ModelParameters/a_seiche` <-  sub$value[3]




write_yaml(yaml, config_file)

export_config(config_file, model)

run_ensemble(config_file, model)

fit <- calc_fit(ncdf, model = model, spin_up = spin_up)
fit # Results from running model with calib output as input
sub # Calibration results

plist <- plot_resid(ncdf = "output/ensemble_output.nc", var = "temp")
ggarrange(plotlist = plist)
# ggsave(file.path(out_f, "calib_results.png"), p1,  dpi = 300,width = 384, height = 280, units = 'mm')


```







Due to our decision to use 2015-2020 as the validation period, we will extend the calibration period 5 years,


```{r, echo = FALSE}

ncdf <- "~/Dropbox/sunapee_LER_projections/LER_calibration/output/ensemble_output_all_models.nc"


######################## Calculating Schmidt Stability ################################


out <- load_var(ncdf = ncdf, var = "temp")
# out <- as.data.frame(out[[1]])
bathy <- read.csv('~/Dropbox/sunapee_LER_projections/LER_inputs/sunapee_hypso.csv')
colnames(bathy) <- c("depths", "areas")
ts.sch <- lapply(out, function(x) {
  ts.schmidt.stability(x, bathy = bathy, na.rm = TRUE)
})
## Reshape to data.frame
df <- melt(ts.sch, id.vars = 1)
colnames(df)[4] <- "model"
df$yday <- yday(df$datetime)
df$year <- year(df$datetime)

df <- df %>% 
  dplyr :: group_by(yday, year) %>% 
  dplyr :: mutate(mean = mean(value, na.rm = TRUE)) %>% 
  dplyr :: mutate(sd = sd(value, na.rm = TRUE))



## plot results
ggplot(df, aes(yday, value, colour = model)) +
  # geom_line(data=df, aes(y=mean, x=yday), color = "black", size = 1) +
  geom_line() +
  # geom_ribbon(data = df, aes(ymin = mean-sd, ymax = mean+sd), alpha = 0.6, 
  #             linetype = 0.1, 
  #             color = "grey") +
  facet_wrap(~year) +
  labs(y = "Schmidt stability (J/m2)") +
  theme_classic() + ylim(-50, 1000) 

ggplot(df, aes(yday, mean)) + 
  geom_line() + 
  geom_ribbon(data = df, aes(ymin = mean-sd, ymax = mean+sd), alpha = 0.6,
              linetype = 0.1,
              color = "grey") + 
  facet_wrap(~year) + 
  labs(y = "Schmidt stability (J/m2)") +
  theme_classic() + ylim(-50, 1000) + 
  geom_line(data = subset(df,  model == "Obs"), aes(yday, value, col = "Obs"))



#################################### Calculating thermocline depth ######################################


## Same for thermocline depth
ts.td <- lapply(out, function(x) {
  ts.thermo.depth(x, Smin = 0.1, na.rm = TRUE)
})

df <- melt(ts.td, id.vars = 1)
colnames(df)[4] <- "model"
df$yday <- yday(df$datetime)
df$month <- month(df$datetime)
df$year <- year(df$datetime)

df <- df %>% 
  dplyr :: group_by(yday, year) %>% 
  dplyr :: mutate(mean = mean(value, na.rm = TRUE)) %>% 
  dplyr :: mutate(sd = sd(value, na.rm = TRUE))

ggplot(subset(df, month >= 6 & month <= 8), aes(yday, value, colour = model)) +
  facet_wrap(~year) +
  geom_line() +
  labs(y = "Thermocline depth (m)") +
  scale_y_continuous(trans = "reverse") +
  theme_classic() 

ggplot(subset(df, month >= 6 & month <= 8 & model != "Obs"), aes(yday, mean)) +
  facet_wrap(~year) +
  geom_line() +
  geom_ribbon(data = subset(df, month >= 6 & month <= 8), aes(ymin = mean-sd, ymax = mean+sd), alpha = 0.6,
              linetype = 0.1,
              color = "grey") + 
  labs(y = "Thermocline depth (m)") +
  scale_y_continuous(trans = "reverse") +
  theme_classic() + 
  geom_line(data = subset(df, month >= 6 & month <= 8 & model == "Obs"), aes(yday, value, col = "Obs"))


dfsummer <- filter(df, month >=6 & month <=8)


# Calculating stratification & ice metrics
temp <- load_var(ncdf, "temp")
ice <- load_var(ncdf, "ice_height")
out <- lapply(1:length(temp), function(x) {
  # x = 1 # for debugging
  mlt <- reshape::melt(temp[[x]], id.vars = 1)
  mlt[, 2] <- as.numeric(gsub("wtr_", "", mlt[, 2]))
  if(names(out)[x] == "Obs") {
    analyse_strat(data = mlt)
  }
  analyse_strat(data = mlt, H_ice = ice[[x]][, 2])
})
names(out) <- names(temp)



df <- melt(out[1:5], id.vars = 1)
colnames(df)[4] <- "model"
ggplot(df, aes(x = year, y = value, col = model)) + geom_line() + 
  facet_wrap(~variable, scales = "free_y")

```


The chunk of code at the end of this script contains the mean, standard deviation and variance calculations across GCMs, RCPs and LER models. I want a method check on this piece of code due to its importance in the scope of this study. The calculations are done by grouping the variable, year, and two of the three columns: rcp, gcm, model. Whichever column is omitted in the grouping is the variable that the mean, sd, and variance is calculated for. 

POST MEETING: The decision for these methods is to separate the chunk into multiple smaller pieces of code so as to avoid potential errors brought by continuously grouping in one pipe. Multiple pipes will create multiple dataframes, which will then be appended to one another. 

```{r, eval = FALSE}

gcm <- c("GFDL-ESM2M", "HadGEM2-ES", "IPSL-CM5A-LR", "MIROC5")
# 
# # List of RCP's to run 
# gcm <- c("GFDL-ESM2M")
rcp <- c("historical", "rcp26", "rcp85")




setwd("~/Dropbox/sunapee_LER_projections/LER_projections/output/")


anomalies_master <- data.frame("year" = numeric(0), "month" = numeric(0), "yday" = numeric(0), 
                               "rcp" = character(0), "gcm" = character(0), "model" = character(0), "variable" = character(0),
                               "value" = numeric(0), "mean" = numeric(0), "anom" = numeric(0))


  for(i in 1:length(gcm)){
    # Sets working directory to each gcm 
    # Nested for loop goes into RCP scenarios for GCMs 
    for(l in 1:length(rcp)){
      ncdf <- paste0(gcm[[i]], "_", rcp[[l]], "_output.nc")
      print(ncdf)
      
      out <- load_var(ncdf = ncdf, var = "temp")
      #out <- as.data.frame(out[[1]])
      bathy <- read.csv('~/Dropbox/sunapee_LER_projections/LER_inputs/sunapee_hypso.csv')
      colnames(bathy) <- c("depths", "areas")
      ts.sch <- lapply(out, function(x) {
        ts.schmidt.stability(x, bathy = bathy, na.rm = TRUE)
      })
      ## Reshape to data.frame
      df <- melt(ts.sch, id.vars = 1)
      colnames(df)[4] <- "model"
      df$yday <- yday(df$datetime)
      df$year <- year(df$datetime)
      df$month <- month(df$datetime)
      df$gcm <- gcm[[i]]
      df$rcp <- rcp[[l]]

      if(rcp[[l]] == "historical"){
            hmeans <- df %>%  dplyr::group_by(model, gcm, rcp) %>% 
            dplyr::mutate(mean = mean(value, na.rm = TRUE))
            
            mean_all <- hmeans %>% 
              dplyr::filter(model != "Obs") %>% 
              distinct(mean, .keep_all = TRUE) %>% 
              # mutate(gcm = gcm[[i]],
              #        rcp = rcp[[l]]) %>% 
              select(variable, model, mean, gcm)
      }
        
            

      else{
        
        anomalies <- merge(mean_all, df, by = c("variable", "model", "gcm"
                                                )) %>% 
          mutate(anom = value - mean) %>%
          dplyr::filter(model != "Obs") %>% 
          select(year, month, yday, rcp.y, gcm, model, 
                 variable, value, mean, anom)
          colnames(anomalies)[4] <- c("rcp")
          
        
        anomalies$variable <- as.character(anomalies$variable)
        
        anomalies_master <- rbind(anomalies_master, anomalies)





        }
      

      }
    }
  


  
anomalies_by_year <- anomalies_master %>% group_by(year, rcp, gcm, model, variable, mean) %>% 
  summarise(across(where(is.numeric), ~mean(.x, na.rm = TRUE)))
  

#separate out into separate dataframes 
anomalies_master <- anomalies_by_year %>% 
  group_by(rcp, gcm, variable, year) %>% 
  dplyr::mutate(mean_model = mean(anom, na.rm = TRUE)) %>%
  dplyr::mutate(sd_model = sd(anom, na.rm = TRUE)) %>% 
  dplyr::mutate(var_model = var(anom, na.rm = TRUE)) %>%
  group_by(rcp, model, variable, year) %>%
  dplyr::mutate(mean_gcm = mean(anom, na.rm = TRUE)) %>%
  dplyr::mutate(sd_gcm = sd(anom, na.rm = TRUE)) %>% 
  dplyr::mutate(var_gcm = var(anom, na.rm = TRUE)) %>%
  group_by(gcm, model, variable, year) %>% 
  dplyr::mutate(mean_rcp = mean(anom, na.rm = TRUE)) %>% 
  dplyr::mutate(sd_rcp = sd(anom, na.rm = TRUE)) %>% 
  dplyr::mutate(var_rcp = var(anom, na.rm = TRUE))

  

```

It was discussed during the meeting that the variance plot demonstrating contribution to uncertainty cannot contain RCP scenario uncertainty. This is because the RCP scenario uncertainty 


```{r}

setwd("~/Dropbox/sunapee_LER_projections/anomaly_calculations/")

anomalies_by_year <- read.csv("schmidt_annual_anomalies.csv")
anomalies_by_year


ggplot(anomalies_by_year, aes(year, anom, colour = model)) +
  facet_wrap(gcm~rcp, scale = "free") +
  geom_line() +
  labs(y = "Schmidt stability (J/m2)") +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model), alpha = 0.4,
              linetype = 0.1,
              color = "grey") 

ggplot(anomalies_by_year, aes(x = year, y = mean_model, col = gcm)) +
  geom_line() +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model, fill = gcm), alpha = 0.2,
              linetype = .1) +
  facet_wrap(~rcp)  
  
# 
# ggplot(anomalies_by_year, aes(x = year, y = mean_gcm, col = model)) +
#   geom_line() +
#   geom_ribbon(data = anomalies_by_year, aes(ymin = mean_gcm-sd_gcm, ymax = mean_gcm+sd_gcm), alpha = 0.4,
#               linetype = 0.1,
#               col = "grey") + 
#   facet_wrap(~rcp)
# 


ggplot(anomalies_by_year, aes(x = year, y = var_model, col = "model")) + geom_point()+
  geom_point(data = anomalies_by_year, aes(x = year, y = var_gcm, col = "gcm")) 



anom_midcentury <- anomalies_by_year %>% filter(year >= 2020 & year <= 2050 & rcp == "rcp85") 
anom_endcentury <- anomalies_by_year %>% filter(year >= 2069 & year <= 2099 & rcp == "rcp85")
print(paste0("The mean midcentury Schmidt Stability for rcp8.5 is: ", mean(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The mean endcentury Schmidt Stability for rcp8.5 is: ", mean(anom_endcentury$anom, na.rm = TRUE)))
print(paste0("The maximum midcentury Schmidt Stability for rcp8.5 is: ", max(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The maximum endcentury Schmidt Stability for rcp8.5 is: ", max(anom_endcentury$anom, na.rm = TRUE)))
print(paste0("The minimum midcentury Schmidt Stability for rcp8.5 is: ", min(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The minimum endcentury Schmidt Stability for rcp8.5 is: ", min(anom_endcentury$anom, na.rm = TRUE)))

```

Do way more than 3 years for spin up 

average across gcm and model, color by rcp, use polygon to plot the rcp, ribbon represents the upper and lower limits of the rcp (y upper and y lower) 


```{r}

setwd("~/Dropbox/sunapee_LER_projections/anomaly_calculations/")

anomalies_by_year <- read.csv("thermodepth_annual_anomalies.csv")
anomalies_by_year



ggplot(anomalies_by_year, aes(year, anom, colour = model)) +
  facet_wrap(gcm~rcp) +
  geom_line() +
  labs(y = "Schmidt stability (J/m2)") +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model), alpha = 0.4,
              linetype = 0.1,
              color = "grey") 

ggplot(anomalies_by_year, aes(x = year, y = mean_model, col = gcm)) +
  geom_line() +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model, fill = gcm), alpha = 0.2,
              linetype = .1) +
  facet_wrap(~rcp)  
  
# 
# ggplot(anomalies_by_year, aes(x = year, y = mean_gcm, col = model)) +
#   geom_line() +
#   geom_ribbon(data = anomalies_by_year, aes(ymin = mean_gcm-sd_gcm, ymax = mean_gcm+sd_gcm), alpha = 0.4,
#               linetype = 0.1,
#               col = "grey") + 
#   facet_wrap(~rcp)
# 


ggplot(anomalies_by_year, aes(x = year, y = var_model, col = "model")) + geom_point()+
  geom_point(data = anomalies_by_year, aes(x = year, y = var_gcm, col = "gcm")) 





anom_midcentury <- anomalies_by_year %>% filter(year >= 2020 & year <= 2050 & rcp == "rcp85") 
anom_endcentury <- anomalies_by_year %>% filter(year >= 2069 & year <= 2099 & rcp == "rcp85")
print(paste0("The mean midcentury thermocline depth for rcp8.5 is: ", mean(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The mean endcentury thermocline depth for rcp8.5 is: ", mean(anom_endcentury$anom, na.rm = TRUE)))
print(paste0("The maximum midcentury thermocline depth for rcp8.5 is: ", max(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The maximum endcentury thermocline depth for rcp8.5 is: ", max(anom_endcentury$anom, na.rm = TRUE)))
print(paste0("The minimum midcentury thermocline depth for rcp8.5 is: ", min(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The minimum endcentury thermocline depth for rcp8.5 is: ", min(anom_endcentury$anom, na.rm = TRUE)))



```


Below are some example plots of the remaining thermal metric anomalies. After discussions during the meeting, the most important metrics highlighted in the discussion will be chosen based on how comprehensive and important ecologially they are. Current thoughts about these metrics is to include  bottom temperature, surface temperature, total ice duration, and total stratification duration. 


```{r}
setwd("~/Dropbox/sunapee_LER_projections/anomaly_calculations/")

anomalies_by_year <- read.csv("multiple_annual_anomalies.csv")
anomalies_by_year

ggplot(subset(anomalies_by_year, variable == "MeanIceDuration"), aes(year, anom, colour = model)) +
  facet_wrap(gcm~rcp, scales = "free") +
  geom_line() +
  labs(y = "Mean Ice Duration (Days)") +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model), alpha = 0.4,
              linetype = 0.1,
              color = "grey") 

ggplot(subset(anomalies_by_year, variable == "MeanIceDuration"), aes(x = year, y = mean_model, col = gcm)) +
  geom_line() +
  geom_ribbon(data = anomalies_by_year, aes(ymin = mean_model-sd_model, ymax=mean_model+sd_model, fill = gcm), alpha = 0.2,
              linetype = .1) +
  facet_wrap(~rcp)  + 
  ggtitle("Mean Ice Duration (Days)")

ggplot(subset(anomalies_by_year, gcm == "GFDL-ESM2M" & rcp == "rcp26"), aes(x = year, y = anom, col = model)) + geom_line() + 
  facet_wrap(~variable, scales = "free_y") + 
  ggtitle("Anomaly Values under rcp2.6 and GFDL gcm")
  

ggplot(subset(anomalies_by_year, gcm == "GFDL-ESM2M" & rcp == "rcp85"), aes(x = year, y = anom, col = model)) + geom_line() + 
  facet_wrap(~variable, scales = "free_y") + 
  ggtitle("Anomaly Values under rcp8.5 and GFDL gcm")


ggplot(anomalies_by_year, aes(x = year, y = var_model, col = "model")) + geom_point(size = 0.2)+
  geom_point(data = anomalies_by_year, aes(x = year, y = var_gcm, col = "gcm"), size = 0.2) + 
  facet_wrap(~variable, scales = "free")







anom_midcentury <- anomalies_by_year %>% filter(year >= 2020 & year <= 2050 & rcp == "rcp85" & variable == "TbMax") 
anom_endcentury <- anomalies_by_year %>% filter(year >= 2069 & year <= 2099 & rcp == "rcp85" & variable == "TbMax")
print(paste0("The mean midcentury maximum bottom temperature for rcp8.5 is: ", mean(anom_midcentury$anom, na.rm = TRUE)))
print(paste0("The mean endcentury maximum bottom temperature for rcp8.5 is: ", mean(anom_endcentury$anom, na.rm = TRUE)))




```









